
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{fontawesome}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{0.75in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{0.75in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large ABHINAV SINGH}} &
\href{mailto:asingh175@gmail.com}{ \faEnvelope}
{asingh175@gmail.com}
\href{tel:+919455448152}{ \faPhoneSquare}
{+91-9455448152}
\hspace{2pt}
\href{https://github.com/terriblebassist}{\Large \faGithub}
\hspace{2pt}
\href{https://www.linkedin.com/in/abhinavsingh1996/}{\Large \faLinkedinSquare}
\hspace{2pt}
\href{https://terriblebassist-folio.netlify.app}{\Large \faGlobe}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology}{Allahabad, India}
      {Bachelor of Technology in Information Technology;  CGPA: 8.32}{Jul. 2014 -- Jun. 2018}
    \resumeSubheading
      {Ryan International School}{Gurgaon, India}
      {Senior Secondary School;  Score: 96.2\%}{Jun.2013 -- Apr. 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deutsche Bank (DBOI Global Services Pvt. Ltd.)}{Pune, India}
      {Technology Associate, Business Finance}{Mar. 2021 - Present}
      \begin{itemize}
          \item Implemented a single CI/CD jenkins pipeline for efficient and on-demand deployment of applications to openshift container cloud platform.
      \end{itemize}
      
      \resumeSubheading
      {Deutsche Bank (DBOI Global Services Pvt. Ltd.)}{Pune, India}
      {Technology Analyst, Business Finance}{Jul. 2018 - Feb. 2021}
      \begin{itemize}
          \item Worked on \textit{dbPalace} (DB Profit And Loss ACcounting Engine), a one stop shop to view and manage official P\&L production, making the process controlled, efficient and transparent.
          \item Created new financial screens for users, improving visualization \& reducing manual effort drastically.
          \item Migrated monolithic spring applications to spring boot and deployed them to openshift container cloud platform, saving infra costs from hosted servers.
          \item Reduced configuration overhead and mis-configuration issues within the project by migrating environment-based external config to profile-based hierarchical config.
      \end{itemize}
      
    \resumeSubheading
      {Zefo (acquired by Quikr)}{Bangalore, India}
      {SDE Intern}{Jan. 2018 - Jun. 2018}
      \begin{itemize}
          \item Created nRubik, a Google BigQuery powered data warehouse built with data collated from multiple disparate sources, helping automate the manual reporting process and generate insights.
      \end{itemize}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Investscape}
      {Dashboard for tracking mutual fund investments, using python dash and Google Sheets/MongoDB.}
    \resumeSubItem{NAV Seeker}
      {Spring boot RESTful application which fetches latest/historic NAV of any AMFI registered mutual fund and stores them in an in-memory spring cache. }
    \resumeSubItem{Myfolio}
      {Simple responsive portfolio website using Vue, Scrollreveal.js, and Tailwind CSS.}
    \resumeSubItem{Soccer Mine}
      {Basic web crawler which generates and dumps FIFA21 player stats from FifaIndex.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{Java, C++ STL, C, Python, Groovy, MySQL, GraphQL}
    \resumeSubItem{Technologies/Platforms}{SpringBoot, Jenkins, Helm, Docker, Kubernetes, Openshift, Maven, JIRA, Git, Scrum}
 \resumeSubHeadingListEnd


%-------EXTRAS
\section{Leadership \& Volunteer Experience}
  \resumeSubHeadingListStart
      \resumeSubItem{Placement Cell}
      {\textit{(Overall Head Coordinator, 2017-18)} Led the placement core team and successfully coordinated with more than 70 companies for their recruitment drives for the 2017-18 placement season in IIITA.}
      
      \resumeSubItem{Music Society}
      {\textit{(Head Coordinator, 2016-2017)} Organized various music events on an All India level at Effervescence, the annual cultural fest of IIIT Allahabad. Bassist/Pianist in a Hard/Funk Rock band.}
      
      \resumeSubItem{Prayaas}
      {\textit{(Member, 2016-2017)} Volunteer organization maintained by IIIT Allahabad students to try to ameliorate the lives of underprivileged kids around the Jhalwa village by providing them with early primary education.}
    \resumeSubHeadingListEnd
      
      
\section{Extras}
    \resumeSubHeadingListStart
      \resumeSubItem{Scholarship(2014)}{SHE(Scholarship for Higher Education) recipient, Dept. of Science and Technology, India.}
      \resumeSubItem{Travel}{Trekking/hiking enthusiast. Have completed various north himalayan/south-indian treks and trails.}
      \resumeSubItem{Fitness/Sports}{CrossFit enthusiast, Football, Swimming}
      \resumeSubItem{Music}{Piano, Bass Guitar, Bagpipes}
    \resumeSubHeadingListEnd
     
%-------------------------------------------
\end{document}
